Towards Practical First-Order Model Counting

### 2025-06-14 doc/talk/bijections.tex
Better plots

% Created by tikzDevice version 0.12.6 on 2025-06-13 10:38:09
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

@@

\path[draw=drawColor,line width= 0.5pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (307.15,216.81);
\end{scope}
\begin{scope}
\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
\definecolor{fillColor}{gray}{0.92}

\path[fill=fillColor] ( 29.55, 57.56) rectangle (302.65,212.31);
\definecolor{drawColor}{RGB}{255,255,255}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 29.55,196.55) -- ( 35.24,196.55);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (307.15,216.81);
\definecolor{drawColor}{gray}{0.30}

>>>>

% Created by tikzDevice version 0.12.6 on 2025-06-14 12:11:57
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

@@

\path[draw=drawColor,line width= 0.5pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (307.15,216.81);
\end{scope}
\begin{scope}
\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 29.55, 57.56) rectangle (302.65,212.31);
\definecolor{drawColor}{gray}{0.92}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 29.55,196.55) -- ( 35.24,196.55);
\definecolor{drawColor}{RGB}{169,169,169}

\path[draw=drawColor,line width= 0.6pt,line join=round] (154.81,156.33) -- (290.23,156.33);

\path[draw=drawColor,line width= 0.6pt,line join=round] (170.46,165.36) --
	(154.81,156.33) --
	(170.46,147.29);

\path[draw=drawColor,line width= 0.6pt,line join=round] (274.59,147.29) --
	(290.23,156.33) --
	(274.59,165.36);

\path[draw=drawColor,line width= 0.6pt,line join=round] (154.81,156.33) -- (290.23,156.33);

\path[draw=drawColor,line width= 0.6pt,line join=round] (170.46,165.36) --
	(154.81,156.33) --
	(170.46,147.29);

\path[draw=drawColor,line width= 0.6pt,line join=round] (274.59,147.29) --
	(290.23,156.33) --
	(274.59,165.36);

\path[draw=drawColor,line width= 0.6pt,line join=round] (154.81,156.33) -- (290.23,156.33);

\path[draw=drawColor,line width= 0.6pt,line join=round] (170.46,165.36) --
	(154.81,156.33) --
	(170.46,147.29);

\path[draw=drawColor,line width= 0.6pt,line join=round] (274.59,147.29) --
	(290.23,156.33) --
	(274.59,165.36);

\path[draw=drawColor,line width= 0.6pt,line join=round] (154.81,156.33) -- (290.23,156.33);

\path[draw=drawColor,line width= 0.6pt,line join=round] (170.46,165.36) --
	(154.81,156.33) --
	(170.46,147.29);

\path[draw=drawColor,line width= 0.6pt,line join=round] (274.59,147.29) --
	(290.23,156.33) --
	(274.59,165.36);

\path[draw=drawColor,line width= 0.6pt,line join=round] (154.81,156.33) -- (290.23,156.33);

\path[draw=drawColor,line width= 0.6pt,line join=round] (170.46,165.36) --
	(154.81,156.33) --
	(170.46,147.29);

\path[draw=drawColor,line width= 0.6pt,line join=round] (274.59,147.29) --
	(290.23,156.33) --
	(274.59,165.36);

\path[draw=drawColor,line width= 0.6pt,line join=round] (154.81,156.33) -- (290.23,156.33);

\path[draw=drawColor,line width= 0.6pt,line join=round] (170.46,165.36) --
	(154.81,156.33) --
	(170.46,147.29);

\path[draw=drawColor,line width= 0.6pt,line join=round] (274.59,147.29) --
	(290.23,156.33) --
	(274.59,165.36);

\path[draw=drawColor,line width= 0.6pt,line join=round] (154.81,156.33) -- (290.23,156.33);

\path[draw=drawColor,line width= 0.6pt,line join=round] (170.46,165.36) --
	(154.81,156.33) --
	(170.46,147.29);

\path[draw=drawColor,line width= 0.6pt,line join=round] (274.59,147.29) --
	(290.23,156.33) --
	(274.59,165.36);

\path[draw=drawColor,line width= 0.6pt,line join=round] (154.81,156.33) -- (290.23,156.33);

\path[draw=drawColor,line width= 0.6pt,line join=round] (170.46,165.36) --
	(154.81,156.33) --
	(170.46,147.29);

\path[draw=drawColor,line width= 0.6pt,line join=round] (274.59,147.29) --
	(290.23,156.33) --
	(274.59,165.36);

\path[draw=drawColor,line width= 0.6pt,line join=round] (154.81,156.33) -- (290.23,156.33);

\path[draw=drawColor,line width= 0.6pt,line join=round] (170.46,165.36) --
	(154.81,156.33) --
	(170.46,147.29);

\path[draw=drawColor,line width= 0.6pt,line join=round] (274.59,147.29) --
	(290.23,156.33) --
	(274.59,165.36);

\path[draw=drawColor,line width= 0.6pt,line join=round] (154.81,156.33) -- (290.23,156.33);

\path[draw=drawColor,line width= 0.6pt,line join=round] (170.46,165.36) --
	(154.81,156.33) --
	(170.46,147.29);

\path[draw=drawColor,line width= 0.6pt,line join=round] (274.59,147.29) --
	(290.23,156.33) --
	(274.59,165.36);

\path[draw=drawColor,line width= 0.6pt,line join=round] (154.81,156.33) -- (290.23,156.33);

\path[draw=drawColor,line width= 0.6pt,line join=round] (170.46,165.36) --
	(154.81,156.33) --
	(170.46,147.29);

\path[draw=drawColor,line width= 0.6pt,line join=round] (274.59,147.29) --
	(290.23,156.33) --
	(274.59,165.36);

\path[draw=drawColor,line width= 0.6pt,line join=round] (154.81,156.33) -- (290.23,156.33);

\path[draw=drawColor,line width= 0.6pt,line join=round] (170.46,165.36) --
	(154.81,156.33) --
	(170.46,147.29);

\path[draw=drawColor,line width= 0.6pt,line join=round] (274.59,147.29) --
	(290.23,156.33) --
	(274.59,165.36);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 7pt off 3pt ,line join=round] (154.81,156.33) -- (290.23,156.33);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 7pt off 3pt ,line join=round] (170.46,165.36) --
	(154.81,156.33) --
	(170.46,147.29);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 7pt off 3pt ,line join=round] (274.59,147.29) --
	(290.23,156.33) --
	(274.59,165.36);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 7pt off 3pt ,line join=round] (154.81,156.33) -- (290.23,156.33);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 7pt off 3pt ,line join=round] (170.46,165.36) --
	(154.81,156.33) --
	(170.46,147.29);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 7pt off 3pt ,line join=round] (274.59,147.29) --
	(290.23,156.33) --
	(274.59,165.36);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 7pt off 3pt ,line join=round] (154.81,156.33) -- (290.23,156.33);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 7pt off 3pt ,line join=round] (170.46,165.36) --
	(154.81,156.33) --
	(170.46,147.29);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 7pt off 3pt ,line join=round] (274.59,147.29) --
	(290.23,156.33) --
	(274.59,165.36);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 7pt off 3pt ,line join=round] (154.81,156.33) -- (290.23,156.33);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 7pt off 3pt ,line join=round] (170.46,165.36) --
	(154.81,156.33) --
	(170.46,147.29);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 7pt off 3pt ,line join=round] (274.59,147.29) --
	(290.23,156.33) --
	(274.59,165.36);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 7pt off 3pt ,line join=round] (154.81,156.33) -- (290.23,156.33);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 7pt off 3pt ,line join=round] (170.46,165.36) --
	(154.81,156.33) --
	(170.46,147.29);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 7pt off 3pt ,line join=round] (274.59,147.29) --
	(290.23,156.33) --
	(274.59,165.36);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 7pt off 3pt ,line join=round] (154.81,156.33) -- (290.23,156.33);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 7pt off 3pt ,line join=round] (170.46,165.36) --
	(154.81,156.33) --
	(170.46,147.29);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 7pt off 3pt ,line join=round] (274.59,147.29) --
	(290.23,156.33) --
	(274.59,165.36);
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (211.38,149.20) --
	(233.67,149.20) --
	(233.59,149.20) --
	(233.91,149.21) --
	(234.22,149.28) --
	(234.52,149.39) --
	(234.80,149.55) --
	(235.05,149.76) --
	(235.26,150.00) --
	(235.43,150.27) --
	(235.56,150.56) --
	(235.63,150.87) --
	(235.66,151.19) --
	(235.66,151.19) --
	(235.66,161.46) --
	(235.66,161.46) --
	(235.63,161.78) --
	(235.56,162.09) --
	(235.43,162.38) --
	(235.26,162.66) --
	(235.05,162.90) --
	(234.80,163.10) --
	(234.52,163.26) --
	(234.22,163.37) --
	(233.91,163.44) --
	(233.67,163.45) --
	(211.38,163.45) --
	(211.62,163.44) --
	(211.30,163.45) --
	(210.98,163.41) --
	(210.67,163.32) --
	(210.38,163.19) --
	(210.12,163.00) --
	(209.89,162.78) --
	(209.69,162.52) --
	(209.54,162.24) --
	(209.44,161.94) --
	(209.39,161.62) --
	(209.38,161.46) --
	(209.38,151.19) --
	(209.39,151.36) --
	(209.39,151.03) --
	(209.44,150.72) --
	(209.54,150.41) --
	(209.69,150.13) --
	(209.89,149.87) --
	(210.12,149.65) --
	(210.38,149.47) --
	(210.67,149.33) --
	(210.98,149.24) --
	(211.30,149.20) --
	cycle;
\end{scope}
\begin{scope}
\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
\definecolor{drawColor}{RGB}{169,169,169}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (222.52,152.52) {$64 \times$};
\end{scope}
\begin{scope}
\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
\definecolor{drawColor}{RGB}{169,169,169}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (211.38,149.20) --
	(233.67,149.20) --
	(233.59,149.20) --
	(233.91,149.21) --
	(234.22,149.28) --
	(234.52,149.39) --
	(234.80,149.55) --
	(235.05,149.76) --
	(235.26,150.00) --
	(235.43,150.27) --
	(235.56,150.56) --
	(235.63,150.87) --
	(235.66,151.19) --
	(235.66,151.19) --
	(235.66,161.46) --
	(235.66,161.46) --
	(235.63,161.78) --
	(235.56,162.09) --
	(235.43,162.38) --
	(235.26,162.66) --
	(235.05,162.90) --
	(234.80,163.10) --
	(234.52,163.26) --
	(234.22,163.37) --
	(233.91,163.44) --
	(233.67,163.45) --
	(211.38,163.45) --
	(211.62,163.44) --
	(211.30,163.45) --
	(210.98,163.41) --
	(210.67,163.32) --
	(210.38,163.19) --
	(210.12,163.00) --
	(209.89,162.78) --
	(209.69,162.52) --
	(209.54,162.24) --
	(209.44,161.94) --
	(209.39,161.62) --
	(209.38,161.46) --
	(209.38,151.19) --
	(209.39,151.36) --
	(209.39,151.03) --
	(209.44,150.72) --
	(209.54,150.41) --
	(209.69,150.13) --
	(209.89,149.87) --
	(210.12,149.65) --
	(210.38,149.47) --
	(210.67,149.33) --
	(210.98,149.24) --
	(211.30,149.20) --
	cycle;
\end{scope}
\begin{scope}
\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
\definecolor{drawColor}{RGB}{169,169,169}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (222.52,152.52) {$64 \times$};
\end{scope}
\begin{scope}
\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
\definecolor{drawColor}{RGB}{169,169,169}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (211.38,149.20) --
	(233.67,149.20) --
	(233.59,149.20) --
	(233.91,149.21) --
	(234.22,149.28) --
	(234.52,149.39) --
	(234.80,149.55) --
	(235.05,149.76) --
	(235.26,150.00) --
	(235.43,150.27) --
	(235.56,150.56) --
	(235.63,150.87) --
	(235.66,151.19) --
	(235.66,151.19) --
	(235.66,161.46) --
	(235.66,161.46) --
	(235.63,161.78) --
	(235.56,162.09) --
	(235.43,162.38) --
	(235.26,162.66) --
	(235.05,162.90) --
	(234.80,163.10) --
	(234.52,163.26) --
	(234.22,163.37) --
	(233.91,163.44) --
	(233.67,163.45) --
	(211.38,163.45) --
	(211.62,163.44) --
	(211.30,163.45) --
	(210.98,163.41) --
	(210.67,163.32) --
	(210.38,163.19) --
	(210.12,163.00) --
	(209.89,162.78) --
	(209.69,162.52) --
	(209.54,162.24) --
	(209.44,161.94) --
	(209.39,161.62) --
	(209.38,161.46) --
	(209.38,151.19) --
	(209.39,151.36) --
	(209.39,151.03) --
	(209.44,150.72) --
	(209.54,150.41) --
	(209.69,150.13) --
	(209.89,149.87) --
	(210.12,149.65) --
	(210.38,149.47) --
	(210.67,149.33) --
	(210.98,149.24) --
	(211.30,149.20) --
	cycle;
\end{scope}
\begin{scope}
\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
\definecolor{drawColor}{RGB}{169,169,169}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (222.52,152.52) {$64 \times$};
\end{scope}
\begin{scope}
\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
\definecolor{drawColor}{RGB}{169,169,169}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (211.38,149.20) --
	(233.67,149.20) --
	(233.59,149.20) --
	(233.91,149.21) --
	(234.22,149.28) --
	(234.52,149.39) --
	(234.80,149.55) --
	(235.05,149.76) --
	(235.26,150.00) --
	(235.43,150.27) --
	(235.56,150.56) --
	(235.63,150.87) --
	(235.66,151.19) --
	(235.66,151.19) --
	(235.66,161.46) --
	(235.66,161.46) --
	(235.63,161.78) --
	(235.56,162.09) --
	(235.43,162.38) --
	(235.26,162.66) --
	(235.05,162.90) --
	(234.80,163.10) --
	(234.52,163.26) --
	(234.22,163.37) --
	(233.91,163.44) --
	(233.67,163.45) --
	(211.38,163.45) --
	(211.62,163.44) --
	(211.30,163.45) --
	(210.98,163.41) --
	(210.67,163.32) --
	(210.38,163.19) --
	(210.12,163.00) --
	(209.89,162.78) --
	(209.69,162.52) --
	(209.54,162.24) --
	(209.44,161.94) --
	(209.39,161.62) --
	(209.38,161.46) --
	(209.38,151.19) --
	(209.39,151.36) --
	(209.39,151.03) --
	(209.44,150.72) --
	(209.54,150.41) --
	(209.69,150.13) --
	(209.89,149.87) --
	(210.12,149.65) --
	(210.38,149.47) --
	(210.67,149.33) --
	(210.98,149.24) --
	(211.30,149.20) --
	cycle;
\end{scope}
\begin{scope}
\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
\definecolor{drawColor}{RGB}{169,169,169}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (222.52,152.52) {$64 \times$};
\end{scope}
\begin{scope}
\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
\definecolor{drawColor}{RGB}{169,169,169}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (211.38,149.20) --
	(233.67,149.20) --
	(233.59,149.20) --
	(233.91,149.21) --
	(234.22,149.28) --
	(234.52,149.39) --
	(234.80,149.55) --
	(235.05,149.76) --
	(235.26,150.00) --
	(235.43,150.27) --
	(235.56,150.56) --
	(235.63,150.87) --
	(235.66,151.19) --
	(235.66,151.19) --
	(235.66,161.46) --
	(235.66,161.46) --
	(235.63,161.78) --
	(235.56,162.09) --
	(235.43,162.38) --
	(235.26,162.66) --
	(235.05,162.90) --
	(234.80,163.10) --
	(234.52,163.26) --
	(234.22,163.37) --
	(233.91,163.44) --
	(233.67,163.45) --
	(211.38,163.45) --
	(211.62,163.44) --
	(211.30,163.45) --
	(210.98,163.41) --
	(210.67,163.32) --
	(210.38,163.19) --
	(210.12,163.00) --
	(209.89,162.78) --
	(209.69,162.52) --
	(209.54,162.24) --
	(209.44,161.94) --
	(209.39,161.62) --
	(209.38,161.46) --
	(209.38,151.19) --
	(209.39,151.36) --
	(209.39,151.03) --
	(209.44,150.72) --
	(209.54,150.41) --
	(209.69,150.13) --
	(209.89,149.87) --
	(210.12,149.65) --
	(210.38,149.47) --
	(210.67,149.33) --
	(210.98,149.24) --
	(211.30,149.20) --
	cycle;
\end{scope}
\begin{scope}
\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
\definecolor{drawColor}{RGB}{169,169,169}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (222.52,152.52) {$64 \times$};
\end{scope}
\begin{scope}
\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
\definecolor{drawColor}{RGB}{169,169,169}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (211.38,149.20) --
	(233.67,149.20) --
	(233.59,149.20) --
	(233.91,149.21) --
	(234.22,149.28) --
	(234.52,149.39) --
	(234.80,149.55) --
	(235.05,149.76) --
	(235.26,150.00) --
	(235.43,150.27) --
	(235.56,150.56) --
	(235.63,150.87) --
	(235.66,151.19) --
	(235.66,151.19) --
	(235.66,161.46) --
	(235.66,161.46) --
	(235.63,161.78) --
	(235.56,162.09) --
	(235.43,162.38) --
	(235.26,162.66) --
	(235.05,162.90) --
	(234.80,163.10) --
	(234.52,163.26) --
	(234.22,163.37) --
	(233.91,163.44) --
	(233.67,163.45) --
	(211.38,163.45) --
	(211.62,163.44) --
	(211.30,163.45) --
	(210.98,163.41) --
	(210.67,163.32) --
	(210.38,163.19) --
	(210.12,163.00) --
	(209.89,162.78) --
	(209.69,162.52) --
	(209.54,162.24) --
	(209.44,161.94) --
	(209.39,161.62) --
	(209.38,161.46) --
	(209.38,151.19) --
	(209.39,151.36) --
	(209.39,151.03) --
	(209.44,150.72) --
	(209.54,150.41) --
	(209.69,150.13) --
	(209.89,149.87) --
	(210.12,149.65) --
	(210.38,149.47) --
	(210.67,149.33) --
	(210.98,149.24) --
	(211.30,149.20) --
	cycle;
\end{scope}
\begin{scope}
\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
\definecolor{drawColor}{RGB}{169,169,169}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (222.52,152.52) {$64 \times$};
\end{scope}
\begin{scope}
\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
\definecolor{drawColor}{RGB}{169,169,169}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (211.38,149.20) --
	(233.67,149.20) --
	(233.59,149.20) --
	(233.91,149.21) --
	(234.22,149.28) --
	(234.52,149.39) --
	(234.80,149.55) --
	(235.05,149.76) --
	(235.26,150.00) --
	(235.43,150.27) --
	(235.56,150.56) --
	(235.63,150.87) --
	(235.66,151.19) --
	(235.66,151.19) --
	(235.66,161.46) --
	(235.66,161.46) --
	(235.63,161.78) --
	(235.56,162.09) --
	(235.43,162.38) --
	(235.26,162.66) --
	(235.05,162.90) --
	(234.80,163.10) --
	(234.52,163.26) --
	(234.22,163.37) --
	(233.91,163.44) --
	(233.67,163.45) --
	(211.38,163.45) --
	(211.62,163.44) --
	(211.30,163.45) --
	(210.98,163.41) --
	(210.67,163.32) --
	(210.38,163.19) --
	(210.12,163.00) --
	(209.89,162.78) --
	(209.69,162.52) --
	(209.54,162.24) --
	(209.44,161.94) --
	(209.39,161.62) --
	(209.38,161.46) --
	(209.38,151.19) --
	(209.39,151.36) --
	(209.39,151.03) --
	(209.44,150.72) --
	(209.54,150.41) --
	(209.69,150.13) --
	(209.89,149.87) --
	(210.12,149.65) --
	(210.38,149.47) --
	(210.67,149.33) --
	(210.98,149.24) --
	(211.30,149.20) --
	cycle;
\end{scope}
\begin{scope}
\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
\definecolor{drawColor}{RGB}{169,169,169}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (222.52,152.52) {$64 \times$};
\end{scope}
\begin{scope}
\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
\definecolor{drawColor}{RGB}{169,169,169}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (211.38,149.20) --
	(233.67,149.20) --
	(233.59,149.20) --
	(233.91,149.21) --
	(234.22,149.28) --
	(234.52,149.39) --
	(234.80,149.55) --
	(235.05,149.76) --
	(235.26,150.00) --
	(235.43,150.27) --
	(235.56,150.56) --
	(235.63,150.87) --
	(235.66,151.19) --
	(235.66,151.19) --
	(235.66,161.46) --
	(235.66,161.46) --
	(235.63,161.78) --
	(235.56,162.09) --
	(235.43,162.38) --
	(235.26,162.66) --
	(235.05,162.90) --
	(234.80,163.10) --
	(234.52,163.26) --
	(234.22,163.37) --
	(233.91,163.44) --
	(233.67,163.45) --
	(211.38,163.45) --
	(211.62,163.44) --
	(211.30,163.45) --
	(210.98,163.41) --
	(210.67,163.32) --
	(210.38,163.19) --
	(210.12,163.00) --
	(209.89,162.78) --
	(209.69,162.52) --
	(209.54,162.24) --
	(209.44,161.94) --
	(209.39,161.62) --
	(209.38,161.46) --
	(209.38,151.19) --
	(209.39,151.36) --
	(209.39,151.03) --
	(209.44,150.72) --
	(209.54,150.41) --
	(209.69,150.13) --
	(209.89,149.87) --
	(210.12,149.65) --
	(210.38,149.47) --
	(210.67,149.33) --
	(210.98,149.24) --
	(211.30,149.20) --
	cycle;
\end{scope}
\begin{scope}
\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
\definecolor{drawColor}{RGB}{169,169,169}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (222.52,152.52) {$64 \times$};
\end{scope}
\begin{scope}
\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
\definecolor{drawColor}{RGB}{169,169,169}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (211.38,149.20) --
	(233.67,149.20) --
	(233.59,149.20) --
	(233.91,149.21) --
	(234.22,149.28) --
	(234.52,149.39) --
	(234.80,149.55) --
	(235.05,149.76) --
	(235.26,150.00) --
	(235.43,150.27) --
	(235.56,150.56) --
	(235.63,150.87) --
	(235.66,151.19) --
	(235.66,151.19) --
	(235.66,161.46) --
	(235.66,161.46) --
	(235.63,161.78) --
	(235.56,162.09) --
	(235.43,162.38) --
	(235.26,162.66) --
	(235.05,162.90) --
	(234.80,163.10) --
	(234.52,163.26) --
	(234.22,163.37) --
	(233.91,163.44) --
	(233.67,163.45) --
	(211.38,163.45) --
	(211.62,163.44) --
	(211.30,163.45) --
	(210.98,163.41) --
	(210.67,163.32) --
	(210.38,163.19) --
	(210.12,163.00) --
	(209.89,162.78) --
	(209.69,162.52) --
	(209.54,162.24) --
	(209.44,161.94) --
	(209.39,161.62) --
	(209.38,161.46) --
	(209.38,151.19) --
	(209.39,151.36) --
	(209.39,151.03) --
	(209.44,150.72) --
	(209.54,150.41) --
	(209.69,150.13) --
	(209.89,149.87) --
	(210.12,149.65) --
	(210.38,149.47) --
	(210.67,149.33) --
	(210.98,149.24) --
	(211.30,149.20) --
	cycle;
\end{scope}
\begin{scope}
\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
\definecolor{drawColor}{RGB}{169,169,169}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (222.52,152.52) {$64 \times$};
\end{scope}
\begin{scope}
\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
\definecolor{drawColor}{RGB}{169,169,169}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (211.38,149.20) --
	(233.67,149.20) --
	(233.59,149.20) --
	(233.91,149.21) --
	(234.22,149.28) --
	(234.52,149.39) --
	(234.80,149.55) --
	(235.05,149.76) --
	(235.26,150.00) --
	(235.43,150.27) --
	(235.56,150.56) --
	(235.63,150.87) --
	(235.66,151.19) --
	(235.66,151.19) --
	(235.66,161.46) --
	(235.66,161.46) --
	(235.63,161.78) --
	(235.56,162.09) --
	(235.43,162.38) --
	(235.26,162.66) --
	(235.05,162.90) --
	(234.80,163.10) --
	(234.52,163.26) --
	(234.22,163.37) --
	(233.91,163.44) --
	(233.67,163.45) --
	(211.38,163.45) --
	(211.62,163.44) --
	(211.30,163.45) --
	(210.98,163.41) --
	(210.67,163.32) --
	(210.38,163.19) --
	(210.12,163.00) --
	(209.89,162.78) --
	(209.69,162.52) --
	(209.54,162.24) --
	(209.44,161.94) --
	(209.39,161.62) --
	(209.38,161.46) --
	(209.38,151.19) --
	(209.39,151.36) --
	(209.39,151.03) --
	(209.44,150.72) --
	(209.54,150.41) --
	(209.69,150.13) --
	(209.89,149.87) --
	(210.12,149.65) --
	(210.38,149.47) --
	(210.67,149.33) --
	(210.98,149.24) --
	(211.30,149.20) --
	cycle;
\end{scope}
\begin{scope}
\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
\definecolor{drawColor}{RGB}{169,169,169}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (222.52,152.52) {$64 \times$};
\end{scope}
\begin{scope}
\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
\definecolor{drawColor}{RGB}{169,169,169}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (211.38,149.20) --
	(233.67,149.20) --
	(233.59,149.20) --
	(233.91,149.21) --
	(234.22,149.28) --
	(234.52,149.39) --
	(234.80,149.55) --
	(235.05,149.76) --
	(235.26,150.00) --
	(235.43,150.27) --
	(235.56,150.56) --
	(235.63,150.87) --
	(235.66,151.19) --
	(235.66,151.19) --
	(235.66,161.46) --
	(235.66,161.46) --
	(235.63,161.78) --
	(235.56,162.09) --
	(235.43,162.38) --
	(235.26,162.66) --
	(235.05,162.90) --
	(234.80,163.10) --
	(234.52,163.26) --
	(234.22,163.37) --
	(233.91,163.44) --
	(233.67,163.45) --
	(211.38,163.45) --
	(211.62,163.44) --
	(211.30,163.45) --
	(210.98,163.41) --
	(210.67,163.32) --
	(210.38,163.19) --
	(210.12,163.00) --
	(209.89,162.78) --
	(209.69,162.52) --
	(209.54,162.24) --
	(209.44,161.94) --
	(209.39,161.62) --
	(209.38,161.46) --
	(209.38,151.19) --
	(209.39,151.36) --
	(209.39,151.03) --
	(209.44,150.72) --
	(209.54,150.41) --
	(209.69,150.13) --
	(209.89,149.87) --
	(210.12,149.65) --
	(210.38,149.47) --
	(210.67,149.33) --
	(210.98,149.24) --
	(211.30,149.20) --
	cycle;
\end{scope}
\begin{scope}
\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
\definecolor{drawColor}{RGB}{169,169,169}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (222.52,152.52) {$64 \times$};
\end{scope}
\begin{scope}
\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
\definecolor{drawColor}{RGB}{169,169,169}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (211.38,149.20) --
	(233.67,149.20) --
	(233.59,149.20) --
	(233.91,149.21) --
	(234.22,149.28) --
	(234.52,149.39) --
	(234.80,149.55) --
	(235.05,149.76) --
	(235.26,150.00) --
	(235.43,150.27) --
	(235.56,150.56) --
	(235.63,150.87) --
	(235.66,151.19) --
	(235.66,151.19) --
	(235.66,161.46) --
	(235.66,161.46) --
	(235.63,161.78) --
	(235.56,162.09) --
	(235.43,162.38) --
	(235.26,162.66) --
	(235.05,162.90) --
	(234.80,163.10) --
	(234.52,163.26) --
	(234.22,163.37) --
	(233.91,163.44) --
	(233.67,163.45) --
	(211.38,163.45) --
	(211.62,163.44) --
	(211.30,163.45) --
	(210.98,163.41) --
	(210.67,163.32) --
	(210.38,163.19) --
	(210.12,163.00) --
	(209.89,162.78) --
	(209.69,162.52) --
	(209.54,162.24) --
	(209.44,161.94) --
	(209.39,161.62) --
	(209.38,161.46) --
	(209.38,151.19) --
	(209.39,151.36) --
	(209.39,151.03) --
	(209.44,150.72) --
	(209.54,150.41) --
	(209.69,150.13) --
	(209.89,149.87) --
	(210.12,149.65) --
	(210.38,149.47) --
	(210.67,149.33) --
	(210.98,149.24) --
	(211.30,149.20) --
	cycle;
\end{scope}
\begin{scope}
\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
\definecolor{drawColor}{RGB}{169,169,169}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (222.52,152.52) {$64 \times$};
\end{scope}
\begin{scope}
\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
\definecolor{drawColor}{RGB}{169,169,169}
\definecolor{fillColor}{RGB}{255,255,255}
